Estimation of the heat demand

### 2017-10-10 Manuscript/HeatDemandMethodology.tex
(almost) final changes to the code
Most of the bugs have been eliminated

\documentclass[]{article}
\usepackage{amsmath}
\usepackage{verbatim}
\usepackage{algorithmicx}
\usepackage[noend]{algpseudocode}

@@

where the vector $\textbf{p}$ includes the calibration parameters that are part of the heat demand and generation estimation model that is explained in detail in the following sections. A list of the parameters $\textbf{p}$ is shown in Table REF, together with the chosen upper and lower boundaries for the calibration procedure.
\begin{table}
	\centering
	\begin{tabular}{p{3cm}ccp{1.6cm}p{1.6cm}p{1.2cm}}
		\hline 
		Parameter name & Symbol  & Unit & Lower Boundary & Higher Boundary & Optimal value \\ 
		\hline
		Constant HTHR heat demand	 & $\dot{Q}_{k,HTHR}$ & kW & 0 & 1000 & 137 \\ 
		Constant steam demand		 & $\dot{Q}_{k,steam}$ & kW & 0 & 1000 & 177 \\
		Weight factor of the HVAC Re-heater & $f_{HVAC,RH}$ & - & 0.5 & 1 & 0.59 \\ 
		Weight factor of the HVAC Pre-heater & $f_{HVAC,PH}$ & - & 0 & 1 & 0.98 \\ 
		Weight factor of hot water heater & $f_{HWH}$ & - & 0.5 & 1 & 0.71 \\ 
		Weight factor of the galley & $f_{G}$ & - & 0.5 & 1 & 0.55 \\ 
		Weight factor of the other consumers & $f_{Other}$ & - & 0.5 & 1 & 0.27 \\ 
		HTHR inlet temperature & $T_{HTHR,ER1,in}$ & K & 343 & 353 & 345 \\
		Effectiveness of the HTHR HEX & $\epsilon_{HTHR} $ & - & 0.5 & 0.9 & 0.72 \\
		Boiler drum steam storage capacity & $Q_{ab,max}$ & MJ & 100 & 100000 & 5580 \\ 
		Boiler heat rate & $\dot{Q}_{ab,des}$ & kW & 2000 & 8000 & 2920 \\ 
		\hline
	\end{tabular} 
\end{table}

@@

Based on the ship's heat balance, we calculate the heat demand as the sum of the contributions of the following elements:

Given that no direct measurement of these quantities is available, they had to be estimated based on the following assumptions:
\begin{table}
	\centering
	\begin{tabular}{p{3cm}lp{1.6cm}}
		\hline 
		Heat flow name & Equation \\
		\hline
		HVAC Preheater & $\dot{Q}_{HVAC,PH} = f_{HVAC,RH} \dot{Q}_{HVAC,PH,des} \frac{\dot{W}_{HVAC}(t)}{\dot{W}_{HVAC,max}} $ \\
		HVAC Reheater &	$\dot{Q}_{HVAC,RH} = f_{HVAC,PH} \dot{Q}_{HVAC,PH,des} \frac{T_{in} - T_{air,out}(t)}{T_{in} - T_{air,out,des}}$ \\
		Hot water heater& $\dot{Q}_{HWH} = f_{HWH} \dot{Q}_{HWH,des} \Phi_{HWH}(\hat{t})$ \\
		Galley & $\dot{Q}_{G} = f_{G} \dot{Q}_{G,des} \Phi_G(\hat{t})$ \\
		Low temperature tank heating & $\dot{Q}_{TH} = f_{TH} \dot{Q}_{TH} \frac{T_{T} - T_{air,out}(t)}{T_{T} -T_{air,out,des}}$ \\
		HFO tank heating & $\dot{Q}_{HTH} = f_{HTH} \dot{Q}_{HTH} \frac{T_{HT} - T_{air,out}(t)}{T_{HT} - T_{air,out,des}}$ \\
		Machinery space heating & $\dot{Q}_{MSH} = f_{MSH} \dot{Q}_{MSH} \frac{T_{MS} - T_{air,out}(t)}{T_{MS} - T_{air,out,des}}$ \\
		HFO heater & $\dot{Q}_{HH} = \dot{m}_{HFO}(t) c_{p,HFO} (T_{HFO,inj} - T_{HT})$ \\
		\hline
	\end{tabular}
\end{table}

where all $f_i$ factors are treated as calibration parameters. The $\Phi_G(\hat{t})$ and $\Phi_{HWH}(\hat{t})$ functions represent the assumption made on the daily evolution of the heating demand from the galley and the hot water heater respectively. The daily evolutions of the demand are considered to be the same over the whole year of operations and are represented graphically in Figure REF.

@@

where $T_{eg,EGB,out}$ and $T_{eg,EGB,in}$ are measured for all EGBs, $c_{p,eg}$ is assumed to be a function of the exhaust gas composition, and $ \dot{m}_{eg} $ is calculated based on the engine energy and mass balance as described in section REF and in the appendix REF

@@

It is known that the ship heating systems are designed for recovering energy from the high temperature cooling systems of all the ship's engines. However, measurements of this contribution and of other variables that could lead to its straight-forward identification, thus requiring certain assumptions.

\begin{eqnarray}
\dot{Q}_{HTHR} & = & \dot{Q}_{HTHR,ER1} + \dot{Q}_{HTHR,ER2} \\
 & = & \sum_{i=ER1,ER2}{\epsilon_{HTHR} * \dot{m}_{min,HTHR,i} * c_{p,w} * (T_{HT,out,i} - T_{HRHT,i,in})} \label{eqn:HTHR2}
\end{eqnarray}

where the effectiveness of the heat exchanger $\epsilon_{HTHR}$ is considered to be constant and its value is part of the parameter estimation problem. The HT water outlet temperature for each engine room is calculated based on the thermal balance of the engines, and the HR water at the HTHR inlet ($T_{HRHT,ER1,in}$) is considered as a calibration parameter.

@@

where the calibration parameters are the heat storage capacity ($Q_{ab,max}$) and the fixed heat rate ($\dot{Q}_{ab,des}$) of the auxiliary boilers.

\section{Uncertainty quantification}

>>>>

\documentclass[]{article}
\usepackage{amsmath}
\usepackage{verbatim}
\usepackage{algorithmicx}
\usepackage[noend]{algpseudocode}
\usepackage{tabls}

@@

where the vector $\textbf{p}$ includes the calibration parameters that are part of the heat demand and generation estimation model that is explained in detail in the following sections. A list of the parameters $\textbf{p}$ is shown in Table REF, together with the chosen upper and lower boundaries for the calibration procedure.
\begin{table}
	\centering
	\begin{tabular}{p{3cm}ccp{1.6cm}p{1.6cm}p{1.2cm}}
		\hline 
		Parameter name & Symbol  & Unit & Lower Boundary & Higher Boundary & Optimal value \\ 
		\hline
		Constant HTHR heat demand	 & $\dot{Q}_{k,HTHR}$ & kW & 0 & 1000 & 137 \\ 
		Constant steam demand		 & $\dot{Q}_{k,steam}$ & kW & 0 & 1000 & 177 \\
		Weight factor of the HVAC Re-heater & $f_{HVAC,RH}$ & - & 0.5 & 1 & 0.59 \\ 
		Weight factor of the HVAC Pre-heater & $f_{HVAC,PH}$ & - & 0 & 1 & 0.98 \\ 
		Weight factor of hot water heater & $f_{HWH}$ & - & 0.5 & 1 & 0.71 \\ 
		Weight factor of the galley & $f_{G}$ & - & 0.5 & 1 & 0.55 \\ 
		Weight factor of the other consumers & $f_{Other}$ & - & 0.5 & 1 & 0.27 \\ 
		HTHR inlet temperature & $T_{HTHR,ER1,in}$ & K & 343 & 353 & 345 \\
		Effectiveness of the HTHR HEX & $\epsilon_{HTHR} $ & - & 0.5 & 0.9 & 0.72 \\
		Boiler drum steam storage capacity & $Q_{ab,max}$ & MJ & 100 & 100000 & 5580 \\ 
		Boiler heat rate & $\dot{Q}_{ab,des}$ & kW & 2000 & 8000 & 2920 \\ 
		\hline
	\end{tabular}
	\caption{Parameters optimized in the parameter estimation for the heat balance}
	\label{tab:ParameterEstimation} 
\end{table}

@@

We calculated the heat demand as the sum of the contributions of the elements listed in the ship's heat balance documentation. As no direct measurement of these quantities was available in the dataset, they had to be estimated based on the following assumptions:
\begin{table}
	\centering
	{\tablinesep=2ex\tabcolsep=10pt
	\begin{tabular}{p{2.8cm}l}
		\hline 
		Heat flow name & Equation \\
		\hline
		HVAC Preheater & $\dot{Q}_{HVAC,PH} = f_{HVAC,RH} \dot{Q}_{HVAC,PH,des} \dfrac{\dot{W}_{HVAC}(t)}{\dot{W}_{HVAC,max}} $ \\
		HVAC Reheater &	$\dot{Q}_{HVAC,RH} = f_{HVAC,PH} \dot{Q}_{HVAC,PH,des} \dfrac{T_{in} - T_{air,out}(t)}{T_{in} - T_{air,out,des}}$ \\
		Hot water heater& $\dot{Q}_{HWH} = f_{HWH} \dot{Q}_{HWH,des} \Phi_{HWH}(\hat{t})$ \\
		Galley & $\dot{Q}_{G} = f_{G} \dot{Q}_{G,des} \Phi_G(\hat{t})$ \\
		Low temperature tank heating & $\dot{Q}_{TH} = f_{TH} \dot{Q}_{TH} \dfrac{T_{T} - T_{air,out}(t)}{T_{T} -T_{air,out,des}}$ \\
		HFO tank heating & $\dot{Q}_{HTH} = f_{HTH} \dot{Q}_{HTH} \dfrac{T_{HT} - T_{air,out}(t)}{T_{HT} - T_{air,out,des}}$ \\
		Machinery space heating & $\dot{Q}_{MSH} = f_{MSH} \dot{Q}_{MSH} \dfrac{T_{MS} - T_{air,out}(t)}{T_{MS} - T_{air,out,des}}$ \\
		HFO heater & $\dot{Q}_{HH} = \dot{m}_{HFO}(t) c_{p,HFO} (T_{HFO,inj} - T_{HT})$ \\
		\hline
	\end{tabular}}
	\caption{Summary of the heat demand contributions and their calculation}
	\label{tab:HeatDemand}
\end{table}

where all $f_i$ factors are treated as calibration parameters (see table \ref{tab:ParameterEstimation}). The $\Phi_G(\hat{t})$ and $\Phi_{HWH}(\hat{t})$ functions represent the assumption made on the daily evolution of the heating demand from the galley and the hot water heater respectively. The daily evolutions of the demand are considered to be the same over the whole year of operations and are represented graphically in Figure REF.

@@

where $T_{eg,EGB,out}$ and $T_{eg,EGB,in}$ are measured for all EGBs, $c_{p,eg}$ is calculated as a function of the exhaust gas composition and temperature, and $ \dot{m}_{eg} $ is calculated based on the engine energy and mass balance as described in section REF and in the appendix REF

@@

It is known that the ship heating systems are designed for recovering energy from the high temperature cooling systems of all the ship's engines. However, measurements of this contribution and of other variables that could lead to its straight-forward identification are missing. In this work, we calculated the heat exchanged in the two HTHRs according to equation \label{eqn:HTHR2},

\begin{eqnarray}
\dot{Q}_{HTHR} & = & \dot{Q}_{HTHR,ER1} + \dot{Q}_{HTHR,ER2} \label{eqn:HTHR1} \\
 & = & \sum_{i=ER1,ER2}{\epsilon_{HTHR} * \dot{m}_{min,HTHR,i} * c_{p,w} * (T_{HT,out,i} - T_{HRHT,i,in})} \label{eqn:HTHR2}
\end{eqnarray}

where the effectiveness of the heat exchanger $\epsilon_{HTHR}$ is considered to be constant and its value is part of the parameter estimation problem (see table \ref{tab:ParameterEstimation}). The HT water outlet temperature for each engine room is calculated based on the thermal balance of the engines, and the HR water at the HTHR inlet ($T_{HRHT,ER1,in}$) is considered as a calibration parameter.

@@

where the calibration parameters are the heat storage capacity ($Q_{ab,max}$) and the fixed heat rate ($\dot{Q}_{ab,des}$) of the auxiliary boilers (see table \ref{tab:ParameterEstimation}).

\section{Parameter estimation and uncertainty quantification}

The results of the parameter estimation are represented graphically and quantitatively in Figure REF and Table REF.
